Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-26 manuscript.Rmd
Updated final plot.

meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
meta.df$studyType <- rep("meta", nrow(meta.df))

@@

systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))

@@

evidence.df <- rbind(meta.df, rct.df, systematicReview.df, 
     quasi.df)

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT", "Systematic review"))

evidence.df$studyType <- factor(evidence.df$studyType, 
    levels(evidence.df$studyType)[c(1,4,3,2)])

@@

stacked.plot <- ggplot(stacked.df, 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) +
    theme_bw() +
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
    theme(  legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Number of Articles") + 
    xlab("Year") + 
    labs(fill = "") +
    scale_y_continuous(breaks = seq(0,90, 10)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

#df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))

j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)])

df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)

df1.unique <- group_by(df1.reduced, journal) %>% slice(1)
df1.unique$journal <- factor(df1.unique$journal, levels = j.order)

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = journal, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity") +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = journal, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) 
```

@@

target.journals <- df1.reduced 
target.journals$journal <- gsub("\\s+\\d+", "", target.journals$journal)
EBP.df <- left_join(target.journals, evidence.journals, by = c("journal", "studyType")) %>%
    group_by(journal) %>%
    slice(1) %>%
    ungroup %>%
    mutate(Proportion = N.sort/Overall.N) %>%
    rename(Absolute = N.sort)

EBP.df  <- within(EBP.df, quartile <- as.integer(cut(Overall.N, quantile(Overall.N, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

ggplot(EBP.df, aes(Proportion, journal, size = Overall.N, colour=as.factor(quartile))) + 
    theme_bw() + 
    geom_point()

View(df1.reduced)

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

df2 <- data.frame(evidence.journals)

j.order <- unique(df2$journal[order(df2$Overall.N.Strength, decreasing = FALSE)]) 
df2$journal <- factor(df2$journal, levels = j.order)

df2  <- within(df2, quartile <- as.integer(cut(Overall.N.Strength, quantile(Overall.N.Strength, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

df2 <- df2 %>% arrange(desc(Prop)) %>% slice(1:15)

EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published") 
```

>>>>

meta.df <- abstract.df[grep("meta\\s?analysis|metanalysis|systematic\\s?review|meta[-]analysis", abstract.df$abstract), ]
meta.df$studyType <- rep("meta", nrow(meta.df))

@@

#systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
#systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))

@@

evidence.df <- rbind(meta.df, rct.df, 
     quasi.df)

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT"))

evidence.df$studyType <- factor(evidence.df$studyType, 
    levels(evidence.df$studyType)[c(1,3,2)])

@@

stacked.plot <- ggplot(stacked.df, 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) +
    theme_bw() +
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
    theme(  legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Number of Articles") + 
    xlab("Year") + 
    labs(fill = "") +
    scale_y_continuous(breaks = seq(0,90, 10)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

@@

abb <- rename(abb, journal = Journal)

df1.reduced <- left_join(df1.reduced, abb, by = "journal")

j.order <- unique(df1.reduced$Abbrev[order(df1.reduced$N.sort, decreasing = FALSE)])

df1.reduced$Abbrev <- factor(df1.reduced$Abbrev, levels = j.order)

df1.unique <- group_by(df1.reduced, Abbrev) %>% slice(1)
df1.unique$journal <- factor(df1.unique$Abbrev, levels = j.order)

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity") +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) +
    theme(legend.position = c(.65,.7), panel.grid.major.y = element_blank(), 
          legend.title=element_blank())
```

@@

proportionEBP3.df <- proportionEBP2.df[proportionEBP2.df$Journal %in% df1.reduced$journal, ]
proportionEBP3.df$Journal <- factor(proportionEBP3.df$Journal, levels = j.order)

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point() +
    geom_segment(aes(yend = Abbrev, xend = 0)) + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
          panel.grid.major.y = element_blank()) + 
    ylab("") + 
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .05, y = Abbrev, label = journalProp), size = 3) +
    xlim(c(0, .5))

```{r}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```
